Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2016-08-18 rebuttal.tex

\katznote{partial response:} In addition, recognizing that the two reviewers have different styles of reading
and different areas of expertise (as do we as authors), we have added a paragraph at the end
of Section 1 to explain how different types of readers might want to approach this paper.  We do
not believe that there is one single way of organizing it that would satisfy all readers.  We have also
added a longer description of each section at this same place.

\hspace{-0.7cm}Section 2.

\item \emph{I didn't think that the terminology and definitions of ``traditional'' and ``infrastructural'' applications made the 2 categories clear. Firstly, ``traditional'' is a poor choice of term as is not intuitively obvious what types of applications fall into this category. The definition didn't really help me: ``meaning a program that is developed by a user or project to try to answer a science question, usually with some input data needed and some output data produced.'' Very few programs don't require input or output data, so that wasn't helpful to me. Also, ``developed by a [..] project'' seemed to also cover the community applications in the other category (if the community was focussed around a project). Also, the term ``infrastructural'' isn't helpful for defining a type of application, as it suggests to me a generic, underpinning set of software services that can be used to build an application, rather than the application itself. The overloading of the term ``application'' in this category didn't help to clarify the situation for me: ``This allows different sub-applications (that we again refer to as `applications')...''. Is the difference that applications in the 2nd category utilise services provided by an infrastructure that is shared by other applications (and users), unlike those in the first category? There may also be the distinction in that only 2nd category applications are distributed.. but that wasn't clear from the text.}

\textbf{Response:} Although we have retained the terms, we have also modified the definitions and specifically, we have refined the discussion of ``infrastructural'' applications.  We believe that
understanding the types of applications, which may be a multi-stage process (reading the definitions/discussion, then reading about the applications themselves) is important to our discussion and conclusions that occur after the Applications Section.

@@

\item \emph{The survey of applications in Section 2 is interesting, but suffers from using terms that are not well defined (see above for suggested fix).}

\textbf{Response:} \katznote{attention needed here}\jhanote{this should also have been addressed by Omer's work. Omer can you confirm please?} \katznote{no, Omer's work added a better description of the paper at the end of Section 1.}

### 2016-08-18 3dpas_intro.tex

The landscape of scientific and enterprise computing is being fundamentally
altered by prodigious volumes of data.  Occasionally data are often naturally
distributed and have to be processed near their source, and sometimes data that
are localized have to be distributed in order to be processed, either for
reasons of performance or for collaborative analytics.  Further, the variation
of data production rates, data source and destination makes temporal variations
in data properties increasingly important.  With an increase in the importance
of distributed and temporal properties of data, systems and infrastructure
aspects such as resource scheduling, data placement, and transfer decisions that
were statically determinable at small scales emerge as dynamic and important
considerations at large scales of data and distribution.

>>>>

The landscape of scientific and enterprise computing is being fundamentally
altered by prodigious volumes of data.  
%Occasionally data are often naturally
%distributed and have to be processed near their source, and sometimes data that
%are localized have to be distributed in order to be processed, Data can be naturally distributed because they are
%being created in a set of distributed locations, rather than in one place. 
Data can also be transported to be processed in multiple, distributed
locations, rather than being processed near their source, or be brought together for processing at
a particular location. These two orthogonal dimensions lead to a number of patterns of data
generation and processing being present in real applications,
either for reasons of performance or for collaborative analytics.  
Further, the variation of data production rates, data source and destination makes 
temporal variations in data properties increasingly important.  
With an increase in the importance of distributed and temporal properties of 
data, systems and infrastructure aspects such as resource scheduling, d
ata placement, and transfer decisions that
were statically determinable at small scales emerge as dynamic and important
considerations at large scales of data and distribution.
